### 2020-04-14 prep.tex
Sort by last name

\section*{Conference Organization}
	\addcontentsline{toc}{chapter}{Conference Organization}
	\subsection*{Organising committee}
	\begin{compactitem}[]
		\item[] Jan Albert Van Laar, chair (University of Groningen)
		\item[] Henrike Jansen (University of Leiden)
		\item[] Catarina Dutilh Novaes (Vrije Universiteit Amsterdam)
		\item[] Bart Verheij (University of Groningen)
	\end{compactitem}

	\subsection*{Programme committee}
	\begin{compactitem}[]
		\item[] Dale Hample, chair (University of Maryland)
		\item[] Henrike Jansen, secretary (University of Leiden)
		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
		\item[] Frank Zenker (Lund University)
		\item[] Juho Ritola (University of Turku)
 	\end{compactitem}

 	\subsection*{ECA steering committee}
 	\begin{compactitem}[]
		\item[] Fabio Paglieri, chair (ISTC-CNR)
		\item[] Jan Albert Van Laar (deputy chair) (University of Groningen)
		\item[] Lilian Bermejo Luque (University of Granada)
		\item[] Katarzyna Budzyńska (Polish Academy of Sciences)
		\item[] Henrike Jansen (University of Leiden)
		\item[] Marcin Koszowy (University of Białystok)
		\item[] Marcin Lewiński (Universidade Nova de Lisboa)
		\item[] Dima Mohammed (Universidade Nova de Lisboa)
		\item[] Steve Oswald (University of Fribourg)
		\item[] Juho Ritola (University of Turku)
		\item[]Sara Rubinelli (University of Lucerne)
		\item[] Frank Zenker (University of Lund)
	\end{compactitem}

@@

		\item[] Hen Jans (University of Leiden)
		\item[] Lotte Van Poppel (University of Amsterdam)
		\item[] Maarten van Leeuwen (Leiden University Centre for Linguistics) (LUCL)

@@

@@

>>>>

\section*{Conference Organization}
	\addcontentsline{toc}{chapter}{Conference Organization}
	\subsection*{Organising committee}
	\begin{compactitem}[]
		\item[] Catarina Dutilh Novaes (Vrije Universiteit Amsterdam)
		\item[] Henrike Jansen (University of Leiden)
		\item[] Jan Albert Van Laar, chair (University of Groningen)
		\item[] Bart Verheij (University of Groningen)
	\end{compactitem}

	\subsection*{Programme committee}
	\begin{compactitem}[]
		\item[] Dale Hample, chair (University of Maryland)
		\item[] Henrike Jansen, secretary (University of Leiden)
		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
		\item[] Juho Ritola (University of Turku)
		\item[] Frank Zenker (Lund University)
 	\end{compactitem}

 	\subsection*{ECA steering committee}
 	\begin{compactitem}[]
		\item[] Lilian Bermejo Luque (University of Granada)
		\item[] Katarzyna Budzyńska (Polish Academy of Sciences)
		\item[] Henrike Jansen (University of Leiden)
		\item[] Marcin Koszowy (University of Białystok)
		\item[] Jan Albert Van Laar, deputy chair (University of Groningen)
		\item[] Marcin Lewiński (Universidade Nova de Lisboa)
		\item[] Dima Mohammed (Universidade Nova de Lisboa)
		\item[] Steve Oswald (University of Fribourg)
		\item[] Fabio Paglieri, chair (ISTC-CNR)
		\item[] Juho Ritola (University of Turku)
		\item[] Sara Rubinelli (University of Lucerne)
		\item[] Frank Zenker (University of Lund)
	\end{compactitem}

@@

@@

		\item[] Henrike Jansen (University of Leiden)
		\item[] Maarten van Leeuwen (Leiden University)

@@

		\item[] Lotte van Poppel (University of Amsterdam)
